---
title: "Group1_HW_Lab7"
output:
  pdf_document: default
  html_notebook: default
editor_options:
  chunk_output_type: inline
---

 Simulate a 90% coverage probability of the normal-based CI
(with unknown population variance) using n = 7 data points
from N(1, 2) distribution. Does your coverage probability.
```{r}
tooLow <- 0           #set counter to 0
tooHigh <- 0          #sest counter to 0
n <- 7               # sample size
N <- 10^5
for (i in 1:N)
 {
  x<-rnorm(n,1,2)
  #x <- rgamma(n, shape=5, rate=2)
  #hist(x)
  xbar <- mean(x)
  s <- sd(x)
  lower <- xbar - abs(qt(.05, n-1))*s/sqrt(n)
  upper <- xbar + abs(qt(.05, n-1))*s/sqrt(n)
  if (upper < 1) tooLow <- tooLow + 1
  if (lower > 1) tooHigh <- tooHigh + 1
 }
tooLow/N
tooHigh/N


```
90% confidence that the coverage probability is  .04943 on the left side and .4967 on the right when the data is normally distributed.


Simulate a 90% coverage probability of the normal-based CI
(with unknown population variance) using n = 5 data points
from rcauchy(n, location=1, scale=2). Does your coverage probability
match the confidence level? Why or why not? Repeat for
n = 30 and ompare results. Interpret.

```{r}
set.seed(1)
tooLow <- 0           #set counter to 0
tooHigh <- 0          #sest counter to 0
n <- 5               # sample size
N <- 10^5
for (i in 1:N)
 {
  x<-rexp(n,2/5)
  #x<-rcauchy(n,1,2)
  #x <- rgamma(n, shape=5, rate=2)
  # hist(x)  DANGER!!!!!!!!!!! DO NOT UNCOMENT!!!!
  xbar <- mean(x)
  s <- sd(x)
  lower <- xbar - abs(qt(.05, n-1))*s/sqrt(n)
  upper <- xbar + abs(qt(.05, n-1))*s/sqrt(n)
  if (upper < 2/5) tooLow <- tooLow + 1
  if (lower > 2/5) tooHigh <- tooHigh + 1
 }
tooLow/N
tooHigh/N


```
For a sample size of 5, I am 90% confidence that the coverage probability is .00011 on the left and .50257 on the right when the data is exponentially distributed.


```{r}
set.seed(1)
tooLow <- 0           #set counter to 0
tooHigh <- 0          #sest counter to 0
n <- 30               # sample size
N <- 10^5
for (i in 1:N)
 {
  x<-rexp(n,30/2)
  #x<-rcauchy(n,1,2)
  #x <- rgamma(n, shape=5, rate=2)
  #hist(x)
  xbar <- mean(x)
  s <- sd(x)
  lower <- xbar - abs(qt(.05, n-1))*s/sqrt(n)
  upper <- xbar + abs(qt(.05, n-1))*s/sqrt(n)
  if (upper < 2/30) tooLow <- tooLow + 1
  if (lower > 2/30) tooHigh <- tooHigh + 1
 }
tooLow/N
tooHigh/N
```
For a sample size of 30, I am 90% confidence that the coverage probability is 0.09818 on the left and 0.02376 on the right when the data is exponentially distributed.
